Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64

### 2018-03-10 PAPER.tex
updated jackknife plot

By-eye inspection of the transfer function plot in Figure \ref{fig:sigloss_transfercurve} gives a sense of what the signal loss result should be. The power spectrum value of our data, $
\widehat{\textbf{p}}_{x}$ is marked by the solid gray horizontal lines. From the left plot (inverse covariance weighting), one can eyeball that a data value of $10^{5} \, mK^{2} (h^{-1} Mpc)^{3}$, for example, would map approximately to a 
value of $\sim10^{8} \, mK^{2} (h^{-1} Mpc)^{3}$, implying a signal loss factor of $\sim1000$. For the uniform-weighted case (right plot), we see no loss at a data value of $\sim10^{7} \, mK^{2} (h^{-1} Mpc)^{3}$.

@@

\begin{figure*}
	\centering
	\includegraphics[width=1\textwidth]{plots/null_zoom.png}
	\caption{Results for three null tests compared to analytically estimated 
$2\sigma$ errors (gray shaded region). For each of the tests, we take a jackknife along a different axis of the dataset - along julian days (separating 
even and odd days; blue), along baselines (green), and along LST (magenta). We expect the sky signal to disappear for a `passing' null test.
We find that the baselines (green) and even/odd (blue) tests are consistent with noise, and that the dominant source of the biases in our power spectrum are likely caused by variation of foregrounds in LST (due to the magenta result being the most inconsistent with noise)}
	\label{fig:null}
\end{figure*}

Investigating Figure \ref{fig:null}, we find that the baselines test is fully consistent with noise (all error bars pass through zero), and that the even/odd test is consistent with noise given the $2\sigma$ expectations ($95\%$ of the error bars are passing through zero). We additionally note that the error bars for the baselines test (green) are especially small --- this is because the signal is effectively cancelled out prior to cross-multiplication (when forming baseline groups).

The null test in LST is much more illuminating. Because of the large error bars and variation in its result, this suggests that the primary systematic driving our power spectrum points and errors to be outside the 
estimated error region is LST-dependent, and therefore likely to be residual foregrounds. In other words, the fact that several magenta power spectrum points, as well as their error bars, are outside the estimated error region implies that $t_{1}$ and 
$t_{2}$ differ by an amount greater than thermal noise and they do not effectively cancel out the sky signal during cross-multiplication. We also note that the LST null test is biased high, consistent with the interpretation that our positive power spectrum detections in Figure \ref{fig:ps1_data} are those of foregrounds.

>>>>

By-eye inspection of the transfer function plot in Figure \ref{fig:sigloss_transfercurve} gives a sense of what the signal loss result should be. The power spectrum value of our data, $
\widehat{\textbf{p}}_{x}$ is marked by the solid gray horizontal lines. From the left plot (inverse covariance weighting), one can eyeball that a data value of $10^{4} \, mK^{2} (h^{-1} Mpc)^{3}$, for example, would map approximately to a 
value of $\sim10^{8} \, mK^{2} (h^{-1} Mpc)^{3}$, implying a signal loss factor of $\sim10000$. For the uniform-weighted case (right plot), we see no loss at a data value of $\sim10^{7} \, mK^{2} (h^{-1} Mpc)^{3}$.

@@

\begin{figure*}
	\centering
	\includegraphics[width=1\textwidth]{plots/null_zoom.png}
	\caption{Power spectrum results for three null tests using $\widehat{\textbf{C}}_{eff}$, compared to the analytically estimated 
$2\sigma$ error (gray shaded region). For each of the tests, we take a jackknife along a different axis of the dataset - along julian days (separating 
even and odd days; blue), along baselines (green), and along LST (magenta). We expect the sky signal to disappear for a `passing' null test.
We find that the baselines (green) and even/odd (blue) tests are consistent with noise, and that the dominant source of the biases in our power spectrum are likely caused by variation of foregrounds in LST (due to the magenta result being the most inconsistent with noise)}
	\label{fig:null}
\end{figure*}

Investigating Figure \ref{fig:null}, we find that the baselines test is fully consistent with noise (all error bars pass through zero), and that the even/odd test is consistent with noise given the $2\sigma$ expectations (nearly $95\%$ of the error bars are passing through zero). We additionally note that the error bars for the baselines test (green) are especially small --- this is because the signal is effectively cancelled out prior to cross-multiplication (when forming baseline groups).

The null test in LST is much more illuminating. Because of the large variable error bars, many of which do not include zero, this suggests that the primary systematic driving our power spectrum points and errors to be outside the 
estimated error region is LST-dependent, and therefore likely to be residual foregrounds. In other words, the fact that several magenta power spectrum points, as well as their error bars, are outside the estimated error region implies that $t_{1}$ and 
$t_{2}$ differ by an amount greater than thermal noise and they do not effectively cancel out the sky signal during cross-multiplication. We also note that the LST null test is biased high, consistent with the interpretation that our positive power spectrum detections in Figure \ref{fig:ps1_data} are those of foregrounds.
